---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# quiltr <img src="man/figures/quiltr_logo.svg" align="right" height="120"/>

[![Build Status](https://travis-ci.org/btmonier/croix.svg?branch=master)](https://travis-ci.org/btmonier/quiltr)
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Overview
This package is used to create randomized, tesselation-based patterns using 
isoceles right triangles. Pattern developments were inspired by quilting 
designs.


## Installation
The current way to install this package is only through GitHub:

```{r, eval=FALSE}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("btmonier/quiltr")
```


## Usage
To get a randomize quilting "data set", simply use the following:

```{r}
qDS <- quiltr::quiltr()
```

With this object, basic S3 methodologies can be implemented:

```{r}
print(qDS)

summary(qDS)
```

Probably the most important method to use would be `plot()`:

```{r}
plot(qDS)
```

To generate larger canvases with customized colors and probabilities, we can
use the following implementation:

```{r}
# Plot with unequal color probabilities
qds <- quiltr::quiltr(
    x    = 10,
    y    = 10,
    col  = c("#DCD0C0", "#C0B283", "#F4F4F4"),
    prob = c(0.2, 0.7, 0.1)
)
plot(qds, sym = "reflect")
```

- - -
*Last updated:* `r format(Sys.Date())`
